---
title: "Contained Metals"
output: html_notebook
---

Counting down the mines with the most metal. 

Using Mining Intelligences tab on Reserves/Resources: http://data.miningintelligence.com/property/browsesearch.aspx?vt=56

Questions to answer: 

-By metal, what mines have the most proven&probable and measured&indicated? 
-What are the stages of these projects? 
-Who owns them? 
-Out of the top ten, what portion of metal do them contain? 
-What geo region are the metals? 

Adding other data.frames for ownership and location. 



```{r}

library(tidyverse)

resraw <- read_csv("C:/Users/Admin/Downloads/resources-report-michael-mccrae-20180409110926 contained metals apr 2018 no ampersand.csv")
View(resraw)

overviewraw <- read_csv("C:/Users/Admin/Downloads/properties-overview-report-michael-mccrae-20180409140956 overview property.csv")
overviewraw

ownershipraw <- read_csv("C:/Users/Admin/Downloads/properties-ownership-report-michael-mccrae-20180409141032 ownership.csv")
ownershipraw


```


Since left_join is killing me, I am going to try plyr's join. 


```{r}

library(plyr)

resprov3 <- join(resraw, overviewraw, type="left", match="first")

resprov4 <- join(resprov3, ownershipraw, type="left", match="first")

View(resprov4)





```


Check if this worked out. Let's count number of projects by commodity with PandP classification. 

```{r}

countcom3 <- resprov4 %>% filter(Classification=="Proven and Probable") %>% dplyr::count(Commodity) %>% arrange(desc(n))

countcom3


```

How about total of copper tonnes? 

```{r}

coppertotal3 <- resprov4 %>% dplyr::filter(Classification=="Proven and Probable") %>% dplyr::filter(Commodity=="Copper") %>% summarise(TotalCommodity=sum(ContainedMetal))

coppertotal3

```



Now, compare to unaltered data set. 


```{r}

countcom11 <- resraw %>% filter(Classification=="Proven and Probable") %>% dplyr::count(Commodity) %>% arrange(desc(n))

countcom11

coppertotal11 <- resraw %>% dplyr::filter(Classification=="Proven and Probable") %>% dplyr::filter(Commodity=="Copper") %>% summarise(TotalCommodity=sum(ContainedMetal))

coppertotal11


```


Let's add a column with company and property


```{r}

resprov5 <- resprov4 %>% unite(companyproperty, c(Company,Property), sep="'s ", remove=FALSE)

resprov5

```



K. Now let's play with this DATA SET!

What are the top nickel projects measured and indicated?

```{r}

nickelcountmi <- resprov5 %>% dplyr::filter(Classification=="Measured and Indicated") %>% dplyr::filter(Commodity=="Nickel") %>% dplyr::arrange(desc(ContainedMetal)) %>% select(Company, Property, Country, Province, ActivityStatus, ContainedMetal) 

View(nickelcountmi)

write.table(x = nickelcountmi, file = "nickel3.csv", sep=",")




```




What are the top nickel projects proven and probable?

```{r}

nickelcountpp <- resprov5 %>% dplyr::filter(Classification=="Proven and Probable") %>% dplyr::filter(Commodity=="Nickel") %>% dplyr::arrange(desc(ContainedMetal)) %>% select(Company, Property, Country, Province, ActivityStatus, ContainedMetal) 

View(nickelcountpp)




```



What is the sum of total nickel measured and indicated? 

```{r}

nickelsummeasured <- resprov5 %>% dplyr::filter(Classification=="Measured and Indicated") %>% dplyr::filter(Commodity=="Nickel") %>% tally(ContainedMetal) 

nickelsummeasured

```



What is the sum of total nickel proven and probable? 

```{r}

nickelsumpp <- resprov5 %>% dplyr::filter(Classification=="Proven and Probable") %>% dplyr::filter(Commodity=="Nickel") %>% tally(ContainedMetal) 

nickelsumpp

```

What is nickel measured and indicated by country? 

```{r}

nickelcountrymi <- resprov5 %>% dplyr::filter(Classification=="Measured and Indicated") %>% dplyr::filter(Commodity=="Nickel") %>% group_by(Country) %>% tally(ContainedMetal) %>% arrange(desc(n))

View(nickelcountrymi)


```


What is nickel proven and probable by country?


```{r}

nickelcountrypp <- resprov5 %>% dplyr::filter(Classification=="Proven and Probable") %>% dplyr::filter(Commodity=="Nickel") %>% group_by(Country) %>% tally(ContainedMetal) %>% arrange(desc(n))

nickelcountrypp


```



K. Let's chart. Let's PP and MI on the same data frame. 



```{r}

nickelmipp <- resprov5 %>% dplyr::filter(Classification=="Measured and Indicated"|Classification=="Proven and Probable") %>% dplyr::filter(Commodity=="Nickel") %>% dplyr::arrange(desc(ContainedMetal)) %>% select(Company, Property, Classification,ContainedMetal) %>% top_n(50)

nickelmipp




```



Let's plot. Grouing PP and MI

```{r}

ggplot(nickelmipp, aes(reorder(Property,ContainedMetal), ContainedMetal, fill=Classification)) +
  geom_bar(stat="identity", position=position_dodge())+
  coord_flip()
 


```


Let's focust on MI top 20

```{r}

library(scales)

nickelcountmi2 <- nickelcountmi %>% top_n(20)

ggplot(nickelcountmi2, aes(reorder(Property,ContainedMetal), ContainedMetal)) +
  geom_bar(stat="identity") +
  #geom_text(aes(label=ContainedMetal), hjust=-.1)+
  xlab("Property") + 
  ylab("Contained Metal in Tonnes") +
  ggtitle("Nickel Projects and Mines Ranked by Measured and Indicated") +
  scale_y_continuous(labels=comma)+
  theme_minimal() +
  coord_flip()




```


Let's map measured and indicated totals by country. 





