---
title: "Contained Metals"
output: html_notebook
---

Counting down the mines with the most metal. 

Using Mining Intelligences tab on Reserves/Resources: http://data.miningintelligence.com/property/browsesearch.aspx?vt=56

Questions to answer: 

-By metal, what mines have the most proven&probable and measured&indicated? 
-What are the stages of these projects? 
-Who owns them? 
-Out of the top ten, what portion of metal do them contain? 
-What geo region are the metals? 



```{r}

library(tidyverse)

resraw <- read_csv("C:/Users/Admin/Downloads/resources-report-michael-mccrae-20180409110926 contained metals apr 2018 no ampersand.csv")
resraw





```


Let's count. 

How many Proven and Probable projects are there by commodities? 


```{r}

countcom <- resraw %>% filter(Classification=="Proven and Probable") %>% count(Commodity) %>% arrange(desc(n))

countcom


```




What is the total Contained Metal Proven and Probable by commodities? 

Use ContainedMetalUnits filter to get gold, base metal and other. 

```{r}

totalcom <- resraw %>% filter(Classification=="Proven and Probable") %>% filter(ContainedMetalUnits=="ozt") %>% group_by(Commodity) %>% summarise(TotalCommodity=sum(ContainedMetal)) %>% arrange(desc(TotalCommodity))

totalcom



```



Let's get the top 10 properties by commodity group for just Proven and Probable and precious. 

```{r}

prove20 <- resraw %>% filter(Classification=="Proven and Probable") %>% filter(ContainedMetalUnits=="ozt") %>% select(Property, Commodity, ContainedMetal) %>% group_by(Commodity) %>% top_n(10, ContainedMetal)

View(prove20)



```

Let's chart


```{r}

ggplot(prove20, aes(x=Property, y=ContainedMetal)) +
  geom_bar(stat="identity") +
  coord_flip()+
  facet_wrap(~Commodity, scales="free")


```


I would like to order facets by descending order. I will use instructions at https://drsimonj.svbtle.com/ordering-categories-within-ggplot2-facets

```{r}


###ozt for precious
precious10 <- resraw %>% filter(Classification=="Proven and Probable") %>% filter(ContainedMetalUnits=="ozt") %>% select(Property, Commodity, ContainedMetal)  %>% group_by(Commodity) %>% top_n(10, ContainedMetal) %>% ungroup() %>% arrange(Commodity, ContainedMetal) %>% mutate(order=row_number())

precious10
###t for everything else
base10 <- resraw %>% filter(Classification=="Proven and Probable") %>% filter(ContainedMetalUnits=="t") %>% select(Property, Commodity, ContainedMetal)  %>% group_by(Commodity) %>% top_n(10, ContainedMetal) %>% ungroup() %>% arrange(Commodity, ContainedMetal) %>% mutate(order=row_number())

base10



```


Try faceting again with orders. This is precious 

```{r}

ggplot(precious10, aes(x=order, y=ContainedMetal)) +
  geom_bar(stat="identity") +
  facet_wrap(~Commodity, scales="free") +
# Add categories to axis
  scale_x_continuous(
    breaks = precious10$order,
    labels = precious10$Property,
    expand = c(0,0)
  ) +
  coord_flip()

```





Try faceting again with orders. This is base 

```{r}

ggplot(base10, aes(x=order, y=ContainedMetal)) +
  geom_bar(stat="identity") +
  facet_wrap(~Commodity, scales="free") +
# Add categories to axis
  scale_x_continuous(
    breaks = base10$order,
    labels = base10$Property,
    expand = c(0,0)
  ) +
  coord_flip()

```
