---
title: "Contained Metals"
output: html_notebook
---

Counting down the mines with the most metal. 

Using Mining Intelligences tab on Reserves/Resources: http://data.miningintelligence.com/property/browsesearch.aspx?vt=56

Questions to answer: 

-By metal, what mines have the most proven&probable and measured&indicated? 
-What are the stages of these projects? 
-Who owns them? 
-Out of the top ten, what portion of metal do them contain? 
-What geo region are the metals? 

Adding other data.frames for ownership and location. 



```{r}

library(tidyverse)

resraw <- read_csv(("~/resources-report-michael-mccrae-20180409110926 contained metals apr 2018 no ampersand.csv"))
resraw

overviewraw <- read_csv("~/properties-overview-report-michael-mccrae-20180409140956 overview property.csv")
overviewraw

ownershipraw <- read_csv("~/properties-ownership-report-michael-mccrae-20180409141032 ownership.csv")
ownershipraw


```


Since left_join is killing me, I am going to try plyr's join. 


```{r}

library(plyr)

resprov3 <- join(resraw, overviewraw, type="left", match="first")

resprov4 <- join(resprov3, ownershipraw, type="left", match="first")

resprov4





```


Check if this worked out. Let's count number of projects by commodity with PandP classification. 

```{r}

countcom3 <- resprov4 %>% filter(Classification=="Proven and Probable") %>% dplyr::count(Commodity) %>% arrange(desc(n))

countcom3


```

How about total of copper tonnes? 

```{r}

coppertotal3 <- resprov4 %>% dplyr::filter(Classification=="Proven and Probable") %>% dplyr::filter(Commodity=="Copper") %>% summarise(TotalCommodity=sum(ContainedMetal))

coppertotal3

```



Now, compare to unaltered data set. 


```{r}

countcom11 <- resraw %>% filter(Classification=="Proven and Probable") %>% dplyr::count(Commodity) %>% arrange(desc(n))

countcom11

coppertotal11 <- resraw %>% dplyr::filter(Classification=="Proven and Probable") %>% dplyr::filter(Commodity=="Copper") %>% summarise(TotalCommodity=sum(ContainedMetal))

coppertotal11


```


Let's add a column with company and property


```{r}

resprov5 <- resprov4 %>% unite(companyproperty, c(Company,Property), sep="'s ", remove=FALSE)

resprov5

```



K. Now let's play with this DATA SET!

What are the top copper projects proven and probable?

```{r}

topcopperpp <- resprov5 %>% dplyr::filter(Classification=="Proven and Probable") %>% dplyr::filter(Commodity=="Gold") %>% dplyr::top_n(20, ContainedMetal)






```


Let's plot

```{r}

ggplot(topcopperpp, aes(x=reorder(companyproperty,ContainedMetal), y=ContainedMetal)) +
  geom_bar(stat="identity") +
  coord_flip()
 


```











////////////////////////COPIED OVER CODE FROM VERSION ONE


Let's count. 

How many Proven and Probable projects are there by commodities? 


```{r}

countcom <- resraw %>% filter(Classification=="Proven and Probable") %>% count(Commodity) %>% arrange(desc(n))

countcom


```




What is the total Contained Metal Proven and Probable by commodities? 

Use ContainedMetalUnits filter to get gold, base metal and other. 

```{r}

totalcom <- resraw %>% filter(Classification=="Proven and Probable") %>% filter(ContainedMetalUnits=="ozt") %>% group_by(Commodity) %>% summarise(TotalCommodity=sum(ContainedMetal)) %>% arrange(desc(TotalCommodity))

totalcom



```



Let's get the top 10 properties by commodity group for just Proven and Probable and precious. 

```{r}

prove20 <- resraw %>% filter(Classification=="Proven and Probable") %>% filter(ContainedMetalUnits=="ozt") %>% select(Property, Commodity, ContainedMetal) %>% group_by(Commodity) %>% top_n(10, ContainedMetal)

View(prove20)



```

Let's chart


```{r}

ggplot(prove20, aes(x=Property, y=ContainedMetal)) +
  geom_bar(stat="identity") +
  coord_flip()+
  facet_wrap(~Commodity, scales="free")


```


I would like to order facets by descending order. I will use instructions at https://drsimonj.svbtle.com/ordering-categories-within-ggplot2-facets

```{r}


###ozt for precious
precious10 <- resraw %>% filter(Classification=="Proven and Probable") %>% filter(ContainedMetalUnits=="ozt") %>% select(Property, Commodity, ContainedMetal)  %>% group_by(Commodity) %>% top_n(10, ContainedMetal) %>% ungroup() %>% arrange(Commodity, ContainedMetal) %>% mutate(order=row_number())

precious10
###t for everything else
base10 <- resraw %>% filter(Classification=="Proven and Probable") %>% filter(ContainedMetalUnits=="t") %>% select(Property, Commodity, ContainedMetal)  %>% group_by(Commodity) %>% top_n(10, ContainedMetal) %>% ungroup() %>% arrange(Commodity, ContainedMetal) %>% mutate(order=row_number())

base10



```


Try faceting again with orders. This is precious 

```{r}

ggplot(precious10, aes(x=order, y=ContainedMetal)) +
  geom_bar(stat="identity") +
  facet_wrap(~Commodity, scales="free") +
# Add categories to axis
  scale_x_continuous(
    breaks = precious10$order,
    labels = precious10$Property,
    expand = c(0,0)
  ) +
  coord_flip()

```





Try faceting again with orders. This is base 

```{r}

ggplot(base10, aes(x=order, y=ContainedMetal)) +
  geom_bar(stat="identity") +
  facet_wrap(~Commodity, scales="free") +
# Add categories to axis
  scale_x_continuous(
    breaks = base10$order,
    labels = base10$Property,
    expand = c(0,0)
  ) +
  coord_flip()

```
