---
title: "Contained Metals"
output: html_notebook
---

Counting down the mines with the most metal. 

Using Mining Intelligences tab on Reserves/Resources: http://data.miningintelligence.com/property/browsesearch.aspx?vt=56

Questions to answer: 

-By metal, what mines have the most proven&probable and measured&indicated? 
-What are the stages of these projects? 
-Who owns them? 
-Out of the top ten, what portion of metal do them contain? 
-What geo region are the metals? 

Adding other data.frames for ownership and location. 



```{r}

library(tidyverse)

resraw <- read_csv(("~/resources-report-michael-mccrae-20180409110926 contained metals apr 2018 no ampersand.csv"))
resraw

overviewraw <- read_csv("~/properties-overview-report-michael-mccrae-20180409140956 overview property.csv")
overviewraw

ownershipraw <- read_csv("~/properties-ownership-report-michael-mccrae-20180409141032 ownership.csv")
ownershipraw


```


Since left_join is killing me, I am going to try plyr's join. 


```{r}

library(plyr)

resprov3 <- join(resraw, overviewraw, type="left", match="first")

resprov4 <- join(resprov3, ownershipraw, type="left", match="first")

resprov4





```


Check if this worked out. Let's count number of projects by commodity with PandP classification. 

```{r}

countcom3 <- resprov4 %>% filter(Classification=="Proven and Probable") %>% dplyr::count(Commodity) %>% arrange(desc(n))

countcom3


```

How about total of copper tonnes? 

```{r}

coppertotal3 <- resprov4 %>% dplyr::filter(Classification=="Proven and Probable") %>% dplyr::filter(Commodity=="Copper") %>% summarise(TotalCommodity=sum(ContainedMetal))

coppertotal3

```



Now, compare to unaltered data set. 


```{r}

countcom11 <- resraw %>% filter(Classification=="Proven and Probable") %>% dplyr::count(Commodity) %>% arrange(desc(n))

countcom11

coppertotal11 <- resraw %>% dplyr::filter(Classification=="Proven and Probable") %>% dplyr::filter(Commodity=="Copper") %>% summarise(TotalCommodity=sum(ContainedMetal))

coppertotal11


```


Let's add a column with company and property


```{r}

resprov5 <- resprov4 %>% unite(companyproperty, c(Company,Property), sep="'s ", remove=FALSE)

resprov5

```



K. Now let's play with this DATA SET!

What are the top copper projects proven and probable?

```{r}

exp <- resprov5 %>% dplyr::filter(Classification=="Measured and Indicated") %>% dplyr::filter(Commodity=="Cobalt") %>% group_by(Country, ContainedMetal) %>% summarize()

exp




```


Let's plot

```{r}

ggplot(topcopperpp, aes(x=reorder(Country,ContainedMetal), y=ContainedMetal)) +
  geom_bar(stat="identity") +
  geom_text(aes(label=ContainedMetal))+
  coord_flip()
 


```




